GravExplain: Continuous gravitational wave data analysis in a table-top experiment

### 2020-01-31 paper/paper_main.tex
62nd day of Summer

% AJP requires an abstract for all regular article submissions.
\begin{abstract}
GravExplain

@@

\section{Method and results}
\jam{a previous supervisor hated having subsections right after a section heading, let me know if this displeases you as well}

@@

\subsection{Data capture: webcam}
% how to analyse video, python OpenCV2

@@

\subsection{Tracking tones: the Viterbi algorithm}
% explaination and successful application
\jam{should we introduce viterbi in the introduction, probably?}

\subsection{Advanced data capture: photodiode}
% leave circuit design to an appendix

\subsection{Photodiode viterbi}
\jam{inject simulation wandering tone}

\subsection{Hearing harmonies and chords}
% the best we can do right now
% write about removing mains noise
\jam{this is as far as we go right now}

\subsection{Future work: reconstructing music and voice}
% signal processing required
% may well be a ``future work'' section at the end
\jam{! purely hypothetical right now !}

@@

\appendix
\section{}

>>>>

% AJP requires an abstract for all regular article submissions.
\begin{abstract}
Continuous gravitational wave searches use sophisticated statistical techniques to search for signals in noisy data. We demonstrate some of these techniques in an table-top Michelson interferometer. We also create an optical microphone capable of playing back simple recordings of injected audio.

@@

% \section{Method and results}
\section{Table-top gravitational wave science}

@@

\subsection{Method: webcam}
% how to analyse video, python OpenCV2

@@

\subsection{Advanced method: photodiode and raspberry pi}
% leave circuit design to an appendix
% only briefly mention Salen-Key, leave to signals processing section

\subsection{Tracking tones: the Viterbi algorithm}
% explaination and successful application
% \jam{should we introduce viterbi in the introduction, probably?}

% we can do this with both webcam and photodiode

\section{Optical microphone}
% describe aim of optical microphone: play back injected sounds
% acknowledge problems: fringe counting, transfer function, coupling

\subsection{Signals processing}
% breakdown of model and all of the filters

\subsection{Reconstructing music and voice}
% results of processing, likely mixed with above subsection

@@

\appendix

\newpage
\section{Intensity relation derivation}
\begin{align}
    y_0(t) &= A \sin{(k L - \omega t)} \\
    y_1(t) &= A \sin{(k (L + 2 d \cos{\theta}) - \omega t)} \\
    Y(t) &= A \sin{(k L - \omega t)} + A \sin{(k (L + 2 d \cos{\theta}) - \omega t)} \\
    \phi &= 2 k d \cos{\theta} \\
    Y(t) &= A\; \Im\{e^{i (k L - \omega t)} + e^{i (k L + \phi - \omega t)}\} \\
    Y(t) &= A\; \Im\{e^{i (k L + \phi/2 - \phi/2 - \omega t)} + e^{i (k L + \phi/2 + \phi/2 - \omega t)}\} \\    
    Y(t) &= A\; \Im\{e^{i (k L + \phi/2 - \omega t)} (e^{- i \phi/2} + e^{i \phi/2})\} \\    
    Y(t) &= A\; \Im\{e^{i (k L + \phi/2 - \omega t)} (2 \cos{(\phi/2)})\} \\ 
    Y(t) &= 2 A \cos{(\phi/2)}\; \Im\{e^{i (k L + \phi/2 - \omega t)}\} \\  
    \therefore I(t) &= I_0 \cos^2{(\phi/2)}, \; \phi = \frac{4 \pi \cos{\theta}}{\lambda}\, d(t) \\
    \frac{dI}{dt} &= \frac{dI}{d\phi}\; \frac{d\phi}{dt}\\
    \frac{dI}{d\phi} &= - I_0 \cos{(\phi/2)} \sin{(\phi/2)}\\
    &= - \frac{I_0}{2}\, \sin{(\phi)}\\
    \delta\phi &= \frac{4 \pi \cos{\theta}}{\lambda}\, h\\
    \therefore \delta I &= \frac{- 2 \pi I_0 \cos{\theta}}{\lambda}\,\sin{(\phi_0)}\, h
\end{align}

\section{Circuit design}
% schematic of breadboard and connections to pi
% https://www.circuit-diagram.org/editor/
